Assignment 4

### 2015-02-23 rmtw/a5/latex8.tex
Y O LO

>>>>

kithcneham start

\textbf{Planning the review}
\begin{itemize}
\item Identification of the need for a review (5.1)
Check other SLRs in the field and evaluate them
\item Commissioning a review (5.2)
not needed
\item Specifying the research question(s) (5.3)
this is very impoirtant :)
the search process must identify primary studies htat address the research questions
the data extraction proccess must extract the data items needed to answer the questions
the data analysis process must synthesise the data in such a way that the questions cna b eansewrd.

read the questions in 5.3.1 to come up with similar ones for readability

\item Developing a review protocol (5.4)

\item Evaluating the review protocol (5.5)
\end{itemize}

\textbf{Conducting the review}
\begin{itemize}
\item Identification of research (6.1)
\item Selection of primary studies (6.2)
\item Study quality assessment (6.3)
\item Data extraction and monitoring (6.4)
\item Data synthesis
\end{itemize}

\textbf{Reporting the review}
\begin{itemize}
\item Specifying dissemination mechanisms (7.1)
\item Formatting the main report (7.2)
\item Evaluating the report (7.3)
\end{itemize}
